Applying WaveNet on frequency data

### 2017-01-20 paper/paper.tex
corrected caption of figure 4
added stride section to discussion

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\columnwidth]{figures/pca_explained_variance}
  \caption{Signal compression and denoising using the Daubechies wavelet basis.}
  \label{fig:pca_explained_variance}
\end{figure}

@@

Overlapping chunks of input data turned out to be essential for learning audio features properly. With a stride of 512 (resulting in an overlap of 75\% of neighboring data chunks) results with dynamic volume changes and frequencies within the range $[0, 105]$ within the first seconds of the generated audio could be achieved. Figure \ref{fig:generated_frequencies} visualizes the frequencies of the first 30 seconds of the output. In contrast to that, with a stride of 2048 (meaning no overlap) the network only grasped really frequencies in the range $[0,1.6]$ producing no volume or frequency dynamic in the generated audio at all.\textcolor{red}{Missing for discussion: on the one hand overlap necessary, on the other hand emphasises this to learn constant tones.}\\

@@

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\columnwidth]{figures/pca_explained_variance}
  \caption{Explained variance of the i'th eigenvector in the principal component analysis (with i being the horizontal axis)}
  \label{fig:pca_explained_variance}
\end{figure}

@@

Overlapping chunks of input data turned out to be essential for learning audio features properly. With a stride of 512 (resulting in an overlap of 75\% of neighboring data chunks) results with dynamic volume changes and frequencies within the range $[0, 105]$ within the first seconds of the generated audio could be achieved. Figure \ref{fig:generated_frequencies} visualizes the frequencies of the first 30 seconds of the output. In contrast to that, with a stride of 2048 (meaning no overlap) the network only grasped really frequencies in the range $[0,1.6]$ producing no volume or frequency dynamic in the generated audio at all.\\

@@

It has been shown that the stride is of great importance for the strength of the frequencies. Strong frequencies are interpreted as the network being confident in its prediction while weak frequencies are a sign of uncertainty. When the training timesteps do not overlap (stride = window size), the network produces much weaker frequencies. But a big stride might also lead to what we experience as not-changing frequencies. With a small stride most of the data chunks are the same as the previous one (when the length of a tone is much longer than one time unit). With larger strides, the frequencies change abruptly from one window to another. When a change in frequencies occurrs on an dataset with smaller strides, the absolute value of the difference of frequencies is much smaller.\\
Therefore one can assume that with changing the setting (stride, but also window size, dilations, normalization etc.), also this approach might produce good results.
